AI Safety for High Energy Physics

### 2019-08-01 documentation/manuscript.tex
added Daniel et al. paper
added an abstract

\begin{abstract}
blah
\end{abstract}

@@

>>>>

\begin{abstract}
Since the first application of deep learning on `low-level' features for classification in high energy physics (HEP)~\cite{Baldi:2014kfa}, there has been a rapidly expanding literature on the adaptation of industrial deep learning techniques as well as the development of novel methods.  The overall conclusion from this impressive and extensive set of studies is that rarer and more complex signatures can be identified with the new set of powerful tools from deep learning.  However, there is an unstudied risk associated with the traditional HEP workflow and deep learning with high-dimensional data.  In particular, calibrating and validating deep networks in their natural high dimensionality is not possible and therefore current methods may be biased in ways that are not covered by current uncertainty estimates.  By borrowing ideas from AI safety, we illustrate these potential issues and propose a method to blah.  Last sentence.
\end{abstract}

@@

\textbf{As a counter point to Ref.~\cite{Baldi:2014kfa}.}
